|

### 2020-09-17 paper.Rmd
tweaking discussion

In this paper we have introduced the sage display, as a visualisation technique for reversing
the curse of dimensionality in high dimensional projections, and have shown its utility in applications to analysis tasks found in the natural sciences and machine learning. Our case studies highlight that sage display can reduce the effects of data piling. We showed in the sketches example, that our new display decreases the number of overlapping points between classes and provides
better visual separation between classes compared to the regular tour. Furthermore, unlike some
non-linear dimension reduction (NLDR) techniques like t-SNE, the sage display still gives the viewer an accurate assessment of the size of a cluster, as we saw in our single cell example. Our parameter tuning example highlights that the sage display is linear up to a given effective dimension. As a result, the sage display provides interpretable visualisations while preserving global structure in the high dimensional space, as highlighted in the particle physics example.

@@

Add note on interactivity to tuning paragraph. Add a paragraph on applications

>>>>

In this paper we have introduced the sage display, as a visualisation technique for reversing
the curse of dimensionality in high dimensional projections, and have shown its utility in applications in the natural sciences and machine learning. Our case studies highlight that the radial transformation can reduce the effects of data piling, and in combination with the grand tour our new sage display provides interpretable visualisation, while preserving global structure in high dimensional space.

The sage display can be directly used in exploratory high dimensional data analysis
tasks.
We showed in the sketches example, that sage display decreases the number of overlapping points between classes and provides
better visual separation between classes compared to the regular tour. Furthermore, unlike some
non-linear dimension reduction (NLDR) techniques like t-SNE, the sage display still gives the viewer an accurate assessment of the size of a cluster, and their relative orientation.
The single cell RNA-seq case study uncovered clusters that were originally obscured by data piling but that are close in high dimensional space;

as we saw in our single cell example. Our parameter tuning example highlights that the sage display is linear up to a given effective dimension. As a result, the sage display provides interpretable visualisations while preserving global structure in the high dimensional space, as highlighted in the particle physics example.

@@

Add note on interactivity to tuning paragraph. Add a paragraph on applications, correlation
